### 2022-01-17 response2/response2.tex
Finalize res to q3

>>>>

\subsubsection*{Comment 3 -
\color{RoyalBlue} This paper also discusses the importance of the disorder structure and that the large parameter r\_c often characterizes the high mobility electron gas. The latter is considered short in the present manuscript. However, since the authors clarified specific assumptions in their theoretical model, I believe the paper can be published in its current form. Analyzing the system beyond the approximations made here can be done later.}

While we admit that including an analytical description for the effect of long-range impurity potentials is valuable, we need to mentioned about the previous studies \cite{dini16,endo09} influence our work. In these studies the transport properties of quantum Hall syatems and dressed quantum Hall systems have been investigated with the assumption of short-range impurity potentials.
The main focus of the present study is to utilize the novel Floquet-Drude conductivity method \cite{wackerl20,wackerlthesis20} to describe dressed quantum Hall systems. Since it is required to compare our novel theoritical description of charge transport properties with the previous studies \cite{dini16,endo09} of dressed quantum Hall systems, we adopted the same assumptions and conditions used in previous studies. In addition, analysis of long-range needs the proper treatment of interections. These interactions are a different topic and these effects are not discussed in this work and left as future study.
